QALY Comparison - Living Wage Intervention

### 2023-11-06 minos/testing/QALY_comparison_energyCrises.Rmd
Another one...

```{r}
combined.cost <- combined %>%
  select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  mutate(QALY_value = QALYs * 60000)

>>>>

```{r}
combined.cost <- combined %>%
  #select(-pop_size, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, alive_pop, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * 60000)

### 2023-11-06 minos/testing/QALY_comparison_livingWage.Rmd
Another one...

```{r}
combined.cost <- combined %>%
  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, pop_size, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * 60000)

>>>>

```{r}
combined.cost <- combined %>%
  #select(-alive_pop, -SF_12_MCS, -SF_12_PCS, -utility) %>%
  select(run_id, year, alive_pop, total_boost, intervention, QALYs) %>%
  mutate(QALY_value = QALYs * 60000)
